---
title: "Modeling_Candice"
author: "Candice Yu"
date: "2023-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import data
```{r}
Enrollment_Coef<- read.csv("/Users/candiceyu/Documents/PSTAT296B/Data/Enrollment_Coef.csv")
```

```{r}
#plot scores of interest
plot(lee, snmfl, what = c('cophenetic', 'rss'))
#measures are extractable:
lee$measures$rss
lee$measures$cophenetic
```

```{r}
basismap(lee$fit$`7`)
coefmap(lee$fit$`7`)
```

```{r}
s<- featureScore(lee$fit$`7`)
summary(s)

Features_Num <- extractFeatures(lee$fit$`7`, 0.5)
Features_Num
# extract features that have a relative basis contribution above a threshold of 0.5

extractFeatures(lee$fit$`7`, method = "kim")

extractFeatures(lee$fit$`7`, method = "max")
```

```{r}
feature<- names(Benefit_Dummy2[, c(6:60, 62:95, 100:119)])
Feature_Main <- list(feature[Features_Num[1][[1]]], feature[Features_Num[2][[1]]], 
                     feature[Features_Num[3][[1]]], feature[Features_Num[4][[1]]], 
                     feature[Features_Num[5][[1]]], feature[Features_Num[6][[1]]], 
                     feature[Features_Num[7][[1]]])
Feature_Main
```
- Lots of discrete variables
- Differences between continuous variables are small -> change to different scale? 

- Basis vector 1: Mostly inpatient coverage 
- Basis vector 2: High frequency and low severity benefits  
- Basis vector 3: Extra health services (Vision & fitness) 
- Basis vector 4: Extra health services (Fitness)
- Basis vector 5: Extra health services (Vision & fitness)
- Basis vector 6: indicates no drug coverage
- Basis vector 7: Whether it provides out-of-network service or not and whether they are coinsurance. 


# Simple linear model 
```{r}
Linear_Model <- lm(State_Enrollment ~ Year + `X1` + `X2` + `X3` + `X4` +`X5` + `X6` + `X7` + 
     Star_Rating_3 + Star_Rating_3.5 + Star_Rating_4 + Star_Rating_4.5, 
   weights = 1 / State_Eligibles, 
   data = Enrollment_Coef)
summary(Linear_Model)
```

# Linear Mixed Model

```{r}
star_rating <- read.csv("/Users/candiceyu/Documents/PSTAT296B/Data/Benefit_Total.csv") %>% 
  select('Contract_ID', 'Plan_ID', 'Segment_ID', 'Star_Rating', 'Year')
# Left join on multiple columns
Enrollment_Coef_SR <- merge(x = Enrollment_Coef, y = star_rating, 
                         by = c("Contract_ID", "Plan_ID", "Segment_ID", "Year"), all.x=TRUE)
Enrollment_Coef_SR$Star_Rating[which(is.na(Enrollment_Coef_SR$Star_Rating))] = 0
Enrollment_Coef_SR$Star_Rating<- as.factor(Enrollment_Coef_SR$Star_Rating)
```

```{r}
library(nlme)

model1 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7, 
              data = Enrollment_Coef_SR, random = ~ 1 | Year, weights=~State_Eligibles)
summary(model1)

model2 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7, 
              data = Enrollment_Coef_SR, random = ~ 1 | Year/Star_Rating, weights=~State_Eligibles)
summary(model2)
```
```{r}
anova(model1, model2)
# Adding star_rating as random effect increased AIC/BIC
# Star_Rating has no random effect 
```
```{r}
model3 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7, 
              data = Enrollment_Coef_SR, random = ~ 1 | Year, weights =~State_Eligibles)
summary(model3)

model4 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7, 
              data = Enrollment_Coef_SR, random = ~ 1 | Year/Contract_ID, weights=~State_Eligibles)
summary(model4)
```

```{r}
anova(model3, model4)
# Brand (Contract_ID) is significant 
```


```{r}
model5 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7, 
              data = Enrollment_Coef_SR, random = ~ 1 | Year/Contract_ID, weights=~State_Eligibles)

model6 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7 + 
     Star_Rating_3 + Star_Rating_3.5 + Star_Rating_4 + Star_Rating_4.5, 
     data = Enrollment_Coef_SR, random = ~ 1 | Year/Contract_ID, weights=~State_Eligibles)

model7 <- lme(State_Enrollment ~ X1 + X2 + X3 + X4 + X5 + X6 + X7 + 
     Star_Rating_3 + Star_Rating_3.5 + Star_Rating_4 + Star_Rating_4.5, 
     data = Enrollment_Coef_SR, random = ~ 1 | Year, weights=~State_Eligibles)
summary(model5)
summary(model6)

```
```{r}
anova(model5, model6, model7)
# Star_Rating has significant fixed effect 
# Model 6 has the smallest AIC and BIC
```
```{r}
model <- lme(State_Enrollment ~ 1, 
     data = Enrollment_Coef_SR, random = ~ 1 | Contract_Plan_Segment, weights=~State_Eligibles)
summary(model)
```

